---
title: "OOP project: Epidemiological Simulation of COVID-19 Spread"
author: "Tianyi Li"
date: "6/24/2021"
output: 
  ioslides_presentation:
    theme: united
    highlight: kate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
.libPaths("/Users/tili/miniconda3/envs/OOP_project/lib/R/library")
```

# Epidemiological Simulation 

- In a small island with 16 individuals --> Travel 

```{r load dependencies, results="hide"}
library(R6)
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(stringi)
```

## Create R6 object and set functions to access data within R6 object

```{r creating objects, echo=T}
Individual <- R6Class("Individual", 
                  public = list(
                    initialize = function(id = NA,
                                          x = NA,
                                          y = NA,
                                          age = 0, 
                                          susceptibility = 'normal', 
                                          state = 'healthy', 
                                          type = 'normal', 
                                          iter = 0) {
                      tmp <- paste(sample(c(letters, 0:9), 16, replace=TRUE), collapse="")
                      n <- seq(1, nc <- nchar(tmp), by = 4) 
                      private$id <- paste(substring(tmp, n, c(n[-1]-1, nc)), collapse = "-")
                      private$x <- x
                      private$y <- y
                      private$age <- age
                      private$susceptibility <- susceptibility
                      private$state <- state
                      private$type <- type
                      private$iter <- iter
                    },
                    print = function(...) {
                      cat("Individual" , private$id, "at (", private$x, ",", private$y, "): \n")
                      cat("  age: ", private$age, "\n", sep = "")
                      cat("  type:  ", private$type, "\n", sep = "")
                      cat("  current status:  ", private$state, "\n", sep = "")
                      cat("  iter with current status: ", private$iter, "\n", sep = "")
                    },
                    setAge = function(age = NA) {
                      private$age <- age
                    },
                    get_coord = function() {
                       c(private$x, private$y) 
                    },
                    move_x = function(x = NA) {
                      private$x <- x 
                    },
                    move_y = function(y = NA) {
                      private$y <- y 
                    },
                    move = function(x = NA, y = NA) {
                      private$x <- x 
                      private$y <- y
                    },
                    get_x = function() {
                      private$x 
                    },
                    get_y = function() {
                      private$y 
                    },
                    set_state = function(state = NA) {
                      private$state <- state
                    },
                    get_state = function() {
                      private$state 
                    },
                    get_type = function() {
                      private$type 
                    },
                    set_type = function(type = NA) {
                      private$type <- type
                    }
                  ),
                  private = list(
                    id = NA,
                    age = NA,
                    x = NA,
                    y = NA,
                    susceptibility = 'normal',
                    state = 'healthy',
                    type = 'normal',
                    iter = 0
                  )
)

```

## Create 16 individuals in a list 

> - Arrange individuals in a data frame
> - Store individuals information in to a list for further simulation

```{r creating individuals, echo=T}

world <- matrix(data = NA, ncol = 4, nrow = 4) %>% 
  as.list()

neighbor <- matrix(ncol = 4, nrow = 4) %>% 
  as.data.frame()

index2coords <- function(i, neighbor) {
  y <- ceiling(i / ncol(neighbor))
  x <- i - ((y-1) * ncol(neighbor))
  print(paste0("ind_", i," ", "x = ", x, " ", "y = ", y))
  neighbor[x, y] <- paste0("ind_",i)
  return(neighbor)
}

# coords2index
#coords2index <- function(x, y, neighbor) {
#  index <- ((y - 1) * ncol(neighbor)) + x
#  return(index)
#}

#coord <- function(i, neighbor) {
#  if (i <= ncol(neighbor)) {
#    x <- i
#    y <- 1
#    neighbor[x, y] <- paste0("ind_",i)
#    print(paste0("ind_", i," ", "x = ", x, " ", "y = ", y))
#  } else {
#      ifelse ((i %% ncol(neighbor) == 0), x <- ncol(neighbor), x <- i %% ncol(neighbor))
#      ifelse ((i %% ncol(neighbor) == 0), y <- i %/% ncol(neighbor), y <- (i %/% ncol(neighbor) + 1))
#      neighbor[x,y] <- paste0("ind_",i)
#      print(paste0("ind_", i," ", "x = ", x, " ", "y = ", y))
#  }
#  return(neighbor)
#}

#for (i in 1:16) {
#  ind_i <- Individual$new(
#  age = sample(1:100, replace = T, size = 1)
#  )
#  neighbor <- index2coords(i, neighbor)
#  print(ind_i)
#  world[[i]] <- ind_i
#}

coordin <- matrix(ncol = 4, nrow = 16) %>% 
  as.data.frame() %>% 
  "colnames<-" (c("individual", "x", "y", "state"))

for (i in 1:16) {
  ind_i <- Individual$new(
  age = sample(1:100, replace = T, size = 1)
  )
  neighbor <- index2coords(i, neighbor)
  print(ind_i)
  y <- ceiling(i / ncol(neighbor))
  x <- i - ((y-1) * ncol(neighbor))
  ind_i$move(x,y)
  coordin[i, 1] <- paste0("ind_", i)
  coordin[i, 2] <- x
  coordin[i, 3] <- y
  coordin[i, 4] <- ind_i$get_state()
  world[[i]] <- ind_i
}

```

## Plotting original position of individuals and the state of health

```{r plotting}
theme <- theme(text=element_text(size=10),
               axis.text.x=element_blank(),
               axis.text.y=element_blank(),
               axis.ticks=element_blank(),
               strip.background = element_rect(colour=NA, fill=NA),
               plot.background = element_blank(),
               panel.grid.major = element_blank(),
               panel.grid.minor = element_blank(),
               panel.border = element_blank(),
               axis.line.x = element_line(size=0.4),
               axis.line.y = element_line(size=0.4),
               panel.background = element_blank())

ggplot(coordin, aes(x = x, y = y, col = state, label = individual)) + geom_point(size = 10, col = "#56B4E9") +
  ggrepel::geom_text_repel(data = coordin, aes(label = individual), size = 5, point.padding = 15, min.segment.length = 0,
                           fontface = "bold", show.legend = T) +
  theme + xlab("") + ylab("") + ggtitle("Health state of individuals before travel") +
  guides(colour = guide_legend(title = "Health state", override.aes = list(size = 5)))

t(neighbor)[nrow(neighbor):1,]

```

## Let the individuals travel within the world

> - Store and new coordinates after travelling
> - Plot the new position for all individuals
> - Set one of the individuals infected

```{r simulation of movement}
#world <- matrix(1:100, nrow = 10, byrow = T)

#update <- sample(1:16, replace = F)
#o <- order(update)

world_new <- matrix(data = NA, ncol = 4, nrow = 4) %>% 
  as.list()

#for (i in update) {
#  for (j in o) {
#    y <- ceiling(j / ncol(neighbor))
#    x <- j - ((y-1) * ncol(neighbor))
#    neighbor[x, y] <- paste0("ind_",i)
#    print(ind_i)
#    world_new[[i]] <-ind_i
#  }
#}

coordin_new <- coordin

for (i in 1:16) {
  coordin_new[i, 2] <- sample(1:4, replace = F, size = 1)
  coordin_new[i, 3] <- sample(1:4, replace = F, size = 1)
}

ggplot(coordin_new, aes(x = x, y = y, col = state, label = individual)) + geom_point(size = 10, col = "#56B4E9") +
  ggrepel::geom_text_repel(data = coordin_new, aes(label = individual), size = 5, point.padding = 15, min.segment.length = 0,
                           fontface = "bold", show.legend = T) +
  theme + xlab("") + ylab("") + ggtitle("Health state of individuals after travel") +
  guides(colour = guide_legend(title = "Health state", override.aes = list(size = 5)))

neighbor_new <- neighbor
world_new <- world

#A = list(a1 = C$new(1), a2 = C$new(2))    

#B = list()
#for (name in names(A))
#{
#    B[[name]] = A[[name]]$clone(deep=TRUE)
#}

#print(B[["a1"]]$x) # [1]
#A[["a1"]]$x = 4
#print(B[["a1"]]$x) # [1]

for (i in 1:16) {
  x <- coordin_new[i, 2]
  y <- coordin_new[i, 3]
  print(paste0("ind_", i, " ", "x = ", x, " ", "y = ", y))
  world_new[[i]]$move(x,y)
}

world_new[[1]]$set_type("infected")
```

## Check infection states

> - Individuals with the same coordinate will become infected
> - Change the state of the infected individuals in the original list
> - Plot the individuals'position and the health state

```{r change health status once infected}
coordin_infect <- coordin_new
for(i in 1:16) {
     if (world_new[[i]]$get_type() == "infected") {
        if(coordin_new[[i, 2]] %in% coordin_new$x) {
          subset <- coordin_new %>% filter(coordin_new[[i, 2]] == coordin_new$x)  
          subset <- subset %>% filter(coordin_new[[i, 3]] == subset$y)
        }
        infection <- str_sub(subset$individual, start = 5) %>% as.numeric()
        for (j in infection) {
          world_new[[j]]$set_state("infected")
          world_new[[j]]$set_type("infected") 
        }
        coordin_infect[i, 4] <- world_new[[i]]$get_state()
    } 
}

ggplot(coordin_infect, aes(x = x, y = y, col = state, label = individual)) + geom_point(size = 10) +
  scale_color_manual(values = c("#56B4E9","#D55E00")) + 
  ggrepel::geom_text_repel(data = coordin_infect, aes(label = individual), size = 5, point.padding = 15, min.segment.length = 0,
                           fontface = "bold", show.legend = T) +
  theme + xlab("") + ylab("") + ggtitle("Health state of individuals after travel") +
  guides(colour = guide_legend(title = "Health state", override.aes = list(size = 5)))

```

## Count number of infection

> - Check the state of individual in the original list
> - Count the people with "infected"" state
> - Print the summary results

```{r count infection}
infected <- 0
for (i in 1:16) {
    if (world_new[[i]]$get_state() == "infected") {
      infected <- infected + 1  
    } else {
      infected <- infected
    }
}
print(paste0("Infected number after travel:", " ", infected))
```

## Return home

> - Let the individual return home
> - Plot the individual position and health state

```{r return home}
coordin2 <- coordin_infect 
coordin2$x <- coordin$x
coordin2$y <- coordin$y

ggplot(coordin2, aes(x = x, y = y, col = state, label = individual)) + geom_point(size = 10) +
  scale_color_manual(values = c("#56B4E9","#D55E00")) + 
  ggrepel::geom_text_repel(data = coordin2, aes(label = individual), size = 5, point.padding = 15, min.segment.length = 0,
                           fontface = "bold", show.legend = T) +
  theme + xlab("") + ylab("") + ggtitle("Health state of individuals after 1st travel") +
  guides(colour = guide_legend(title = "Health state", override.aes = list(size = 5)))
```

## Future plan

> - Include the simulation process into a function
> - Increase the size of individuals and repeat the simulation