---
title: 'OOP project: Epidemiological Simulation of COVID-19 Spread'
author: "Tianyi Li"
date: "6/24/2021"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
.libPaths("/Users/tili/miniconda3/envs/OOP/lib/R/library")
```

# Epidemiological Simulation 

> - A small island with 16 individuals --> Travel 
> - Infection spread
> - Count number of infected individuals

```{r load dependencies, include = F}
library(R6)
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(stringi)
```

```{r creating objects, echo = F}
Individual <- R6Class("Individual", 
                  public = list(
                    initialize = function(id = NA,
                                          x = NA,
                                          y = NA,
                                          age = 0, 
                                          susceptibility = 'normal', 
                                          state = 'healthy', 
                                          type = 'normal', 
                                          iter = 0) {
                      tmp <- paste(sample(c(letters, 0:9), 16, replace=TRUE), collapse="")
                      n <- seq(1, nc <- nchar(tmp), by = 4) 
                      private$id <- paste(substring(tmp, n, c(n[-1]-1, nc)), collapse = "-")
                      private$x <- x
                      private$y <- y
                      private$age <- age
                      private$susceptibility <- susceptibility
                      private$state <- state
                      private$type <- type
                      private$iter <- iter
                    },
                    print = function(...) {
                      cat("Individual" , private$id, "at (", private$x, ",", private$y, "): \n")
                      cat("  age: ", private$age, "\n", sep = "")
                      cat("  type:  ", private$type, "\n", sep = "")
                      cat("  current status:  ", private$state, "\n", sep = "")
                      cat("  iter with current status: ", private$iter, "\n", sep = "")
                    },
                    setAge = function(age = NA) {
                      private$age <- age
                    },
                    get_coord = function() {
                       c(private$x, private$y) 
                    },
                    move_x = function(x = NA) {
                      private$x <- x 
                    },
                    move_y = function(y = NA) {
                      private$y <- y 
                    },
                    move = function(x = NA, y = NA) {
                      private$x <- x 
                      private$y <- y
                    },
                    get_x = function() {
                      private$x 
                    },
                    get_y = function() {
                      private$y 
                    },
                    set_state = function(state = NA) {
                      private$state <- state
                    },
                    get_state = function() {
                      private$state 
                    },
                    get_type = function() {
                      private$type 
                    },
                    set_type = function(type = NA) {
                      private$type <- type
                    }
                  ),
                  private = list(
                    id = NA,
                    age = NA,
                    x = NA,
                    y = NA,
                    susceptibility = 'normal',
                    state = 'healthy',
                    type = 'normal',
                    iter = 0
                  )
)

```


# Create 16 individuals in a list 

> - Arrange individuals in a data frame
> - Store individuals information in to a list for further simulation

```{r creating individuals, echo=T}

world <- matrix(data = NA, ncol = 4, nrow = 4) %>% 
  as.list()

neighbor <- matrix(ncol = 4, nrow = 4) %>% 
  as.data.frame()

index2coords <- function(i, neighbor) {
  y <- ceiling(i / ncol(neighbor))
  x <- i - ((y-1) * ncol(neighbor))
  print(paste0("ind_", i," ", "x = ", x, " ", "y = ", y))
  neighbor[x, y] <- paste0("ind_",i)
  return(neighbor)
}

coordin <- matrix(ncol = 4, nrow = 16) %>% 
  as.data.frame() %>% 
  "colnames<-" (c("individual", "x", "y", "state"))

for (i in 1:16) {
  ind_i <- Individual$new(
  age = sample(1:100, replace = T, size = 1)
  )
  neighbor <- index2coords(i, neighbor)
  print(ind_i)
  y <- ceiling(i / ncol(neighbor))
  x <- i - ((y-1) * ncol(neighbor))
  ind_i$move(x,y)
  coordin[i, 1] <- paste0("ind_", i)
  coordin[i, 2] <- x
  coordin[i, 3] <- y
  coordin[i, 4] <- ind_i$get_state()
  world[[i]] <- ind_i
}

world[[1]]

```

# Plotting original position of individuals and the state of health

```{r plotting, echo=T}
theme <- theme(text=element_text(size=15),
               axis.text.x=element_blank(),
               axis.text.y=element_blank(),
               axis.ticks=element_blank(),
               strip.background = element_rect(colour=NA, fill=NA),
               plot.background = element_blank(),
               panel.grid.major = element_blank(),
               panel.grid.minor = element_blank(),
               panel.border = element_blank(),
               axis.line.x = element_line(size=0.4),
               axis.line.y = element_line(size=0.4),
               panel.background = element_blank())

plot_state <- function(coordin) {
  ggplot(coordin, aes(x = x, y = y, col = state, label = individual)) + geom_point(size = 10) +
  scale_color_manual(values = c("#56B4E9","#D55E00")) + 
  ggrepel::geom_text_repel(data = coordin, aes(label = individual), size = 5, point.padding = 15, min.segment.length = 0,
                           fontface = "bold", show.legend = T) +
  theme + xlab("") + ylab("") + ggtitle("Health state of individuals after travel") +
  guides(colour = guide_legend(title = "Health state", override.aes = list(size = 5)))
}


plot_state(coordin)

```

# Let the individuals travel within the world

> - Store and new coordinates after travelling
> - Plot the new position for all individuals
> - Set one of the individuals infected

```{r simulation of movement, echo=T}
world_new <- matrix(data = NA, ncol = 4, nrow = 4) %>% 
  as.list()

coordin1 <- coordin

world_new <- world

move_me <- function(coordin_new) {
  for (i in 1:16) {
  coordin_new[i, 2] <- sample(1:4, replace = F, size = 1)
  coordin_new[i, 3] <- sample(1:4, replace = F, size = 1)
  }
  for (i in 1:16) {
  x <- coordin_new[i, 2]
  y <- coordin_new[i, 3]
  return(coordin_new)
  print(paste0("ind_", i, " ", "x = ", x, " ", "y = ", y))
  world_new[[i]]$move(x,y)
}
}

coordin2 <- move_me(coordin1)  
plot_state(coordin2)

```

> - Introduce a person as infected source

```{r Generate infection, echo=T}
world_new[[1]]$set_type("infected")
world_new[[1]]$set_state("infected")
world_new[[1]]
```


# Check infection states

> - Individuals with the same coordinate will become infected
> - Change the state of the infected individuals in the original list
> - Plot the individuals'position and the health state

```{r change health status once infected, echo=T}

spread <- function(coordin_new, coordin_infect) {
  for(i in 1:16) {
     if (world_new[[i]]$get_type() == "infected") {
        if(coordin_new[[i, 2]] %in% coordin_new$x) {
          subset <- coordin_new %>% filter(coordin_new[[i, 2]] == coordin_new$x)  
          subset <- subset %>% filter(coordin_new[[i, 3]] == subset$y)
        }
        infection <- str_sub(subset$individual, start = 5) %>% as.numeric()
        for (j in infection) {
          world_new[[j]]$set_state("infected")
          world_new[[j]]$set_type("infected") 
        }
        coordin_infect[i, 4] <- world_new[[i]]$get_state()
     } 
  }
  return(coordin_infect)
  return(world_new)
}
coordin3 <- coordin2
coordin3 <- spread(coordin2, coordin3)
plot_state(coordin3)


```

# Count number of infection

> - Check the state of individual in the original list
> - Count the people with "infected" state
> - Print the summary results

```{r count infection, echo=T}

count_infect <- function(world_new) {
  infected <- 0
  for (i in 1:16) {
    if (world_new[[i]]$get_state() == "infected") {
      infected <- infected + 1  
    } else {
      infected <- infected
    }
  }
  print(paste0("Infected number after travel:", " ", infected))
}
infected <- count_infect(world_new)

```

# Return home

> - Let the individual return home
> - Plot the individual position and health state

```{r return home, echo=T}
return_home <- function(coordin_infect, coordin4){
  coordin4 <- coordin_infect
  coordin4$x <- coordin$x
  coordin4$y <- coordin$y
  return(coordin4)
}

coordin4 <- return_home(coordin3, coordin4)
plot_state(coordin4)

```

# Second simulation

> - When the infected people travel again

```{r Second simulation}
coordin5 <- move_me(coordin4)  
plot_state(coordin5)

coordin6 <- coordin5
coordin6 <- spread(coordin5, coordin6)
plot_state(coordin6)

infected <- count_infect(world_new)

coordin7 <- coordin6
coordin7 <- return_home(coordin6, coordin7)
plot_state(coordin7)
```

